### 2021-12-08 input/proposal.tex
meow

\begin{definition}[\label{def:lwo}Stale messages]
  Only the latest broadcast of a \node matters.  A message $m$ conveys
  \underline{s}tale control information $\mathcal{S}(m)$ as soon as
  its broadcaster broadcasts another message: $\mathcal{S}(\alpha_x) =
  \exists \delta_x: b_x(\alpha_x) \rightarrow b_x(\delta_x)$.  A
  \process only delivers or sends messages that it assumes
  \underline{u}p-\underline{t}o-\underline{d}ate.
  % : $s_x(\alpha_s)
  % \implies \delta_s \not\in R_x$.
  For convenience, we define $\textup{minUTD(}D\textup{)} = \min
  \{\alpha_s^d | \alpha_s^d \in D \wedge \delta_s \notin D\}$, and
  $\textup{last(}D\textup{)} = \alpha_s \in D: \nexists \alpha_{s'}
  \in D: d_x(\alpha_s) \rightarrow d_x(\alpha_{s'})$.
  %  \TODO{Only keep last?  Tothink what happens if we keep all as in
%    def now.}
\end{definition}

@@

\begin{definition}[\label{def:fbplus}$\textup{FB}^+$: echos] FB where a
  \process $x$ that receives a staleness notification sends back --~or
  echoes~-- its best up-to-date delivered message: $r_{xy}(\alpha_s)
  \wedge \delta_s \in D_x \implies s_{xy}(\alpha_{s'}^d\oplus
  ^{w_{xy}})$ with $\alpha_{s'^d} = \min D_x \wedge \delta_{s'} \not\in
  D_x$. \TODO{Rework min}
\end{definition}

>>>>

\begin{definition}[\label{def:lwo}Stale messages]
  Only the latest broadcast of a \node matters.  A message $m$ conveys
  \underline{s}tale control information $\mathcal{S}(m)$ as soon as
  its broadcaster broadcasts another message: $\mathcal{S}(\alpha_x) =
  \exists \delta_x: b_x(\alpha_x) \rightarrow b_x(\delta_x)$.  A
  \process only delivers or sends messages that it assumes
  \underline{u}p-\underline{t}o-\underline{d}ate.
  % : $s_x(\alpha_s)
  % \implies \delta_s \not\in R_x$.
  For convenience, we define \TODO{$\textup{minUTD(}D\textup{)} = \min
  \{\alpha_s^d | \alpha_s^d \in D \wedge \delta_s \notin D\}$}, and
  $\textup{last(}D\textup{)} = \alpha_s \in D: \nexists \alpha_{s'}
  \in D: d_x(\alpha_s) \rightarrow d_x(\alpha_{s'})$.
  %  \TODO{Only keep last?  Tothink what happens if we keep all as in
%    def now.}
\end{definition}

@@

\begin{definition}[\label{def:fbplus}$\textup{FB}^+$: echos] FB where
  a \process $x$ that receives but does not deliver a staleness
  notification sends back --~or echoes~-- its best up-to-date
  delivered message:
  $\textup{last}~D_x = \alpha_s^d \wedge \delta_s
  \not\in D_x \wedge d_x(\alpha_s^d)\rightarrow r_{xy}(\delta_{s'}) \implies
  s_{xy}(\alpha_s^d\oplus^{w_{xy}})$.

  % $r_{xy}(\alpha_s)
  % \wedge \delta_s \in D_x \implies s_{xy}(\alpha_{s'}^d\oplus
  % ^{w_{xy}})$ with $\alpha_{s'^d} = \min D_x \wedge \delta_{s'} \not\in
  % D_x$. \TODO{Rework min}

\end{definition}
